### 2014-03-18 HowtoHowtoCapon/submission/submit1/answer/answer.tex
...

\ai{Thank you. We mention in the beginning of section IIA that we pre-steer to every angle and range bin in the image, but will try to express this with greater clarity and emphasize that we are operating in the near field.}

>>>>

\ai{Thank you. We mention in the beginning of section IIA that we pre-steer to every angle and range bin in the image. but will try to express this with greater clarity and emphasize that we are operating in the near field.}
